Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Finishing supplemental tables

```{r}
BA_summary <- phenology_models$model[1]
 <- BA_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Survival") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

>>>>

```{r}
ba_data <- phenology_models$model_data[[1]]
ba_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = ba_data)
ba_summary <- summary(ba_mod)
ba_ktable <- ba_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Breeding arrival") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)

bd_data <- phenology_models$model_data[[2]]
bd_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = ba_data)
bd_summary <- summary(ba_mod)
bd_ktable <- bd_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Breeding departure") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)

ma_data <- phenology_models$model_data[[3]]
ma_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = ma_data)
ma_summary <- summary(ma_mod)
ma_ktable <- ma_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Molt arrival") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)

md_data <- phenology_models$model_data[[4]]
md_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = md_data)
md_summary <- summary(md_mod)
md_ktable <- md_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Molt departure") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)

rbind(ba_ktable, bd_ktable, ma_ktable, md_ktable) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(columns = 1)
```
